EldersAIR: Main analysis - PM/Exposure Outcomes

### 2021-06-11 main_analysis_pm.Rmd
analysis updates

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 18 May 2021"
output: pdf_document
---

@@

summary_data <- analysis_data %>% 
  group_by(area, winter_id, wood_collect_3level) %>% 
  summarize(mean(moisture_ave, na.rm = T),
            median(moisture_ave, na.rm = T))
summary_data
```

>>>>

---
title: 'EldersAIR: Main analysis - PM/Exposure Outcomes'
author: "Ethan Walker"
date: "Started 6 May 2021; Updated 27 May 2021"
output: pdf_document
---

@@

summary_data <- analysis_data %>% 
  group_by(area, winter_id, wood_collect_3level) %>% 
  summarize(`Mean Moisture` = mean(moisture_ave, na.rm = T),
            `Median Moisture` = median(moisture_ave, na.rm = T))
summary_data
```
